landlord

### 2023-01-23 src/landlord.Rmd

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)

@@

>>>>

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)
library(ggplot2)

@@

```{r}
# mean ("mean_metric"), 95th percentile ("perc_metric"), and distribution for sensitivity analysis

#Eviction Notice (normalized, inverted)
mean_eviction <- mean(MSA_landlord_data$eviction_notice_days_normalized_inverted)
mean_eviction

perc_eviction <- quantile(MSA_landlord_data$eviction_notice_days_normalized_inverted, probs = 0.95)
perc_eviction

eviction_distribution <- density(MSA_landlord_data$eviction_notice_days_normalized_inverted)
plot(eviction_distribution)

#Security Deposit Limit
mean_deposit <- mean(MSA_landlord_data$security_depopsit_limit_num)
mean_deposit

perc_deposit <- quantile(MSA_landlord_data$security_depopsit_limit_num, probs = 0.95)
perc_deposit

deposit_distribution <- density(MSA_landlord_data$security_depopsit_limit_num)
plot(deposit_distribution)

```
